\documentclass[9pt,a4paper,withhyper]{altacv}
\usepackage{bookmark}
\geometry{left=1.1cm,right=1.1cm,top=1.5cm,bottom=1cm,columnsep=0.6cm}

\usepackage{paracol}
\usepackage{charter}
\usepackage{hyperref}
\urlstyle{same}
\colorlet{tagline}{black}
\colorlet{heading}{black}
\colorlet{headingrule}{black}
\colorlet{subheading}{black}
\colorlet{accent}{black}
\colorlet{emphasis}{black}
\colorlet{body}{black}

\renewcommand{\itemmarker}{{\small\textbullet}}

\begin{document}
\name{Aaron William Po \\ \large{\vspace{-1em} full stack developer}}

\personalinfo{%
	\email{aaron\_po@msn.com}
	\location{London, ON}
	\github{github.com/aaronpo97}
	\faDesktop\,\,
	\url{aaronwilliampo.com}
}
\makecvheader
\columnratio{0.6}

\begin{paracol}{2}
	\cvsection{About}
	I am a full-stack developer looking to break into the tech industry specializing in Typescript/Javascript development with a passion for creating versatile applications for both client and server environments. 
	\vspace{0.5em}\newline
	Committed to continuous learning and innovation, I thrive in dynamic work environments that foster growth and encourage collaboration. I am eager to contribute my skills and expertise to a team's success while further expanding my knowledge in the field.
		
	\cvsection{Projects}
	\cvsubsection{The Biergarten App}
	\vspace{-0.25em}
	{\small \faCode\,\,\,Next.js, Prisma, Postgres, Tailwind CSS}\newline
	{\small \faDesktop\,\,\,\url{https://thebiergarten.app/}}
			
	\vspace{0.5em}
	\begin{itemize}
		\item An innovative web application designed for beer enthusiasts to connect and share their favorite brews and breweries online, that allows beer lovers to engage with like-minded individuals, discussing and discovering new beer experiences.
		\item Leverages the power of \textbf{Next.js}, \textbf{Prisma}, and \textbf{Neon Postgres} to create a dynamic web application focused on fostering a passionate beer community.
		\item Integrates APIs such as \textbf{Cloudinary}, \textbf{SparkPost}, and \textbf{Mapbox} to enrich the user experience by enabling functionalities like image uploading, email services, and geolocation features.
		\item Uses \textbf{Tailwind CSS}, \textbf{Headless UI}, and \textbf{Daisy UI} to create a visually striking and user-friendly interface, enhancing the overall user experience.
		\item Deployed with \textbf{Vercel} for its fast and seamless deployment process that integrates directly with \textbf{Next.js}.
	\end{itemize}
			  
	\divider
			
	\cvsubsection{SpoonBot}
	\vspace{-0.25em}
	{\small \faCode\,\,\,Next.js, Tailwind CSS, OpenAI}\newline
	{\small \faDesktop\,\,\,\url{https://spoonbot.vercel.app/}}
	\vspace{.50em}
	\begin{itemize}
		\item Spearheaded the development of SpoonBot, a cutting-edge web application powered by OpenAI's \textbf{GPT-3 API}, showcasing its ability to generate restaurant names, detailed restaurant reviews, and enticing restaurant menus.
		\item Implemented robust content moderation features to ensure a safe and respectful user experience, leveraging advanced techniques to detect and prevent offensive or harmful language in user input.
		\item Crafted a visually stunning and responsive user interface by harnessing the power of \textbf{Next.js}, a React-based framework, and seamlessly integrating it with the versatility of \textbf{Tailwind CSS}.
	\end{itemize}
	\divider
	\cvsubsection{DoggoBot}
	\vspace{-0.25em}
	{\small \faCode\,\,\,Node.js, Discord.js}\newline
	{\small \faDesktop\,\,\,\url{https://discord.gg/x22H78aqpa}}
	\vspace{.50em}
	\begin{itemize}
		\item Developed a Discord bot using \textbf{Node.js} and \textbf{Discord.js} to automate tasks and provide entertainment by sending pictures of dogs to designated channels on Discord servers.
		\item Utilized the \textbf{Dog CEO API} to fetch random dog images and send them to Discord channels, showcasing the potential of Discord bots for automating tasks and providing entertainment.
		\item Implemented a scheduling system to send dog images at regular intervals, providing a consistent and engaging user experience.
	\end{itemize}
	\switchcolumn
			
	\cvsection{Education}
	\cvevent{Bachelor of Music}{University of Western Ontario}{2015-2020}{London, ON}
			
	\cvsection{Courses taken}
	\cvevent{The Web Developer Bootcamp}{instructed by Colt Steele on Udemy.com}{Certificate of Completion, 2021}{}
	\begin{itemize}
		\item Covered a wide range of web development topics, including HTML, CSS, JavaScript, Node.js, Express, MongoDB, and RESTful APIs.
	\end{itemize}
	
	\cvsection{Skills}
	\cvsubsection{\faCode\, Core Competencies}
	\begin{itemize}
		\item Quickly learns and applies new technologies and methodologies.
		\item Efficiently manages time, prioritizes tasks, and meets deadlines.
		\item Applies critical thinking skills to evaluate situations and make informed decisions.
		\item Self-motivated and takes initiative for personal and professional growth.
		\item Committed to continuous learning and staying updated with industry trends.
		\item Adapts to changing project requirements and embraces new methodologies.
	\end{itemize}
	
	\divider
		
	\cvsubsection{\faCode\, Technical Skills}
	\begin{itemize}
		\item Proficient in \textbf{Git} for version control, using \textbf{GitHub} for collaboration and code management.
		\item Proficient in \textbf{Next.js} and \textbf{React} for building dynamic and responsive web applications.
		\item Proficient in \textbf{TypeScript} and \textbf{JavaScript} for front-end and back-end development.
		\item Proficient in both SQL and NoSQL databases, including \textbf{PostgreSQL}, and \textbf{MongoDB}.
		\item Proficient in \textbf{Tailwind CSS} for rapid UI development and customization.
		\item Experienced with \textbf{Linux} and \textbf{Bash} scripting.
		\item Experienced with UI component libraries (\textbf{Material-UI}, \textbf{Mantine}) and CSS frameworks (\textbf{Bootstrap}).
		\item Familiar with \textbf{Docker} and \textbf{Kubernetes} for containerization and orchestration.
		\item Strong problem-solving and debugging skills.
		\item Strong understanding of back-end concepts \textbf{RESTful APIs}, \textbf{WebSockets}, and \textbf{GraphQL}.
		\item Strong understanding of front-end principles: \textbf{responsive design}, \textbf{accessibility}, and \textbf{performance optimization}.
	\end{itemize}
\end{paracol}

\newpage

\cvsection{Employment History}

\cvevent{Donation Attendant}{Goodwill Industries -- Ontario Great Lakes}{October 2022 -- present}{London, ON}
\begin{itemize}
	\item Provided exceptional customer service to donors and customers, ensuring a positive and respectful experience.
	\item Maintained a clean and organized work environment, ensuring the safety and comfort of customers and staff.
	\item Assisted in the collection and organization of donations, ensuring the efficient and effective processing of goods.
	\item Collaborated with team members to achieve daily goals and maintain a high standard of service.
\end{itemize}
\divider

\cvevent{Host, Expo and Beer Retail Sales}{Toboggan Brewing Company}{September 2021 -- September 2022}{London, ON}
\begin{itemize}
	\item Worked in a dynamic and fast changing atmosphere, providing exceptional customer service to guests.
	\item Adapted to changing roles and responsibilities, accommodating the needs of the business and team members.
	\item Managed takeout orders and their preparation at the expo stand, ensuring timely and accurate delivery of orders to customers.
	\item Provided exceptional customer service through booking reservations and assisting in events booking.
	\item Assisted in the retail sales of beer and merchandise, ensuring a positive and informative customer experience.
	\item Collaborated with team members to maintain a high standard of service and a positive work environment.
\end{itemize}
\divider

\cvevent{Deliveries and E-commerce Associate}{The Home Depot Canada}{March 2021 -- September 2021}{London ON}
\begin{itemize}
	\item Provided exceptional customer service to customers, ensuring a positive and respectful experience.
	\item Managed the preparation and delivery of online orders, ensuring the accurate and timely delivery of goods.
	\item Assisted in the organization and maintenance of the store, ensuring a clean and organized work environment.
	\item Developed strong communication and teamwork skills, collaborating with team members to achieve daily goals.
	\item Adapted to changing roles and responsibilities, accommodating the needs of the business and team members.
\end{itemize}

\end{document}