\documentclass[9pt,a4paper,ragged2e,withhyper]{altacv}
\geometry{left=1.5cm,right=1.5cm,top=2cm,bottom=1.5cm,columnsep=0.5cm}
\usepackage{paracol}
\usepackage{charter}

\colorlet{name}{black}
\colorlet{tagline}{black}
\colorlet{heading}{black}
\colorlet{headingrule}{black}
\colorlet{subheading}{black}
\colorlet{accent}{black}
\colorlet{emphasis}{black}
\colorlet{body}{black}

\begin{document}
\name{Aaron William Po}
\tagline{Full Stack Developer}

\personalinfo{%
	\email{aaron.po97@gmail.com}
	\location{London, Ontario, Canada}
	\github{aaronpo97}
	\faDesktop\,\,
	\url{https://aaronwilliampo.com}
}
\makecvheader
\columnratio{0.6}

\begin{paracol}{2}
	\cvsection{About}
	I am a developer looking to break into the tech industry specializing in Typescript/Javascript development with a passion for creating versatile applications for both client and server environments.
	\vspace{0.5em}\newline
	Committed to continuous learning and innovation, I thrive in dynamic work environments that foster growth and encourage collaboration. I am eager to contribute my skills and expertise to a team's success while further expanding my knowledge in the field.

	\cvsection{Projects}

	\project{
		The Biergarten App
	}{2022-ongoing}{Next.js, Prisma, Postgres, Tailwind CSS}{https://thebiergarten.app/}{
		\item An innovative web application designed for beer enthusiasts to connect and
		share their favorite brews and breweries online, that allows beer lovers to
		engage with like-minded individuals, discussing and discovering new beer
		experiences.
		\item Leverages the power of \textbf{Next.js}, \textbf{Prisma}, and \textbf{Neon
			Postgres} to create a dynamic web application focused on fostering a passionate
		beer community.
		\item Integrates APIs such as \textbf{Cloudinary}, \textbf{SparkPost}, and
		\textbf{Mapbox} to enrich the user experience by enabling functionalities like
		image uploading, email services, and geolocation features.
		\item Uses \textbf{Tailwind CSS}, \textbf{Headless UI}, and \textbf{Daisy UI} to
		create a visually striking and user-friendly interface, enhancing the overall
		user experience.
		\item Deployed with \textbf{Vercel} for its fast and seamless deployment process that
		integrates directly with \textbf{Next.js}. }

	\divider

	\project{
		SpoonBot
	}{2022-ongoing}{Next.js, Tailwind CSS, OpenAI}{https://spoonbot.vercel.app/}{
		\item Spearheaded the development of SpoonBot, a cutting-edge web application powered
		by OpenAI's \textbf{GPT-3 API}, showcasing its ability to generate restaurant
		names, detailed restaurant reviews, and enticing restaurant menus.
		\item Implemented robust content moderation features to ensure a safe and respectful
		user experience, leveraging advanced techniques to detect and prevent offensive
		or harmful language in user input.
		\item Crafted a visually stunning and responsive user interface by harnessing the
		power of \textbf{Next.js}, a React-based framework, and seamlessly integrating
		it with the versatility of \textbf{Tailwind CSS}. }

	\divider

	\project{DoggoBot}{2022-ongoing}{Node.js, Discord.js}{https://discord.gg/x22H78aqpa}{
		\item Developed a Discord bot using \textbf{Node.js} and \textbf{Discord.js} to
		automate tasks and provide entertainment by sending pictures of dogs to
		designated channels on Discord servers.
		\item Utilized the Dog CEO API to fetch random dog images and send them to Discord
		channels, showcasing the potential of Discord bots for automating tasks and
		providing entertainment.
		\item Implemented a scheduling system to send dog images at regular intervals,
		providing a consistent and engaging user experience.}

	\switchcolumn

	\cvsection{Education}
	\cvevent{Adv. Diploma in Computer Programming and Analysis}{Fanshawe College}{2025-2028 (expected)}{London, ON}
	\cvevent{Bachelor of Arts in Music and Philosophy}{University of Western Ontario}{2015-2020}{London, ON}

	\cvsection{Courses taken}
	\cvevent{The Web Developer Bootcamp}{instructed by Colt Steele on Udemy.com}{2021}{}
	\begin{itemize}
		\item A comprehensive course on full-stack web development, covering front-end and
		      back-end technologies, including HTML, CSS, JavaScript, Node.js, and MongoDB.
	\end{itemize}

	\cvsection{Skills}
	\cvsubsection{Core Competencies}
	\begin{itemize}
		\item Quick to learn new technologies and adapt to changes.
		\item Strong time management and problem-solving abilities.
		\item Self-motivated with a focus on continuous learning.
	\end{itemize}

	\divider

	\cvsubsection{Technical Skills}
	\begin{itemize}
		\item Proficient in \textbf{Git} for version control, using \textbf{GitHub} for
		      collaboration and code management.
		\item Proficient in \textbf{Next.js} and \textbf{React} for building dynamic and
		      responsive web applications.
		\item Proficient in \textbf{TypeScript} and \textbf{JavaScript} for front-end and
		      back-end development.
		\item Proficient in both \textbf{SQL} and \textbf{NoSQL} databases, including
		      \textbf{PostgreSQL}, and \textbf{MongoDB}.
		\item Proficient in \textbf{Tailwind CSS} for rapid UI development and customization.
		\item Familiar with Linux and the command line, using \textbf{Bash} for scripting and
		      automation.
		\item Familiar with \textbf{Docker} and \textbf{Kubernetes} for containerization and
		      orchestration.
		\item Strong problem-solving and debugging skills.
		\item Strong understanding of back-end concepts \textbf{RESTful APIs},
		      \textbf{WebSockets}, and \textbf{GraphQL}.
		\item Strong understanding of front-end principles: \textbf{responsive design},
		      \textbf{accessibility}, and \textbf{performance optimization}.
	\end{itemize}
\end{paracol}

\newpage

% \cvsection{Employment History}

% \cvevent{Donation Attendant}{Goodwill Industries -- Ontario Great Lakes}{October 2022 -- present}{London, ON}
% \begin{itemize}
% 	\item Provided exceptional customer service to donors and customers, ensuring a positive and respectful experience.
% 	\item Maintained a clean and organized work environment, ensuring the safety and comfort of customers and staff.
% 	\item Assisted in the collection and organization of donations, ensuring the efficient and effective processing of goods.
% 	\item Collaborated with team members to achieve daily goals and maintain a high standard of service.
% \end{itemize}
% \divider

% \cvevent{Host, Expo and Beer Retail Sales}{Toboggan Brewing Company}{September 2021 -- September 2022}{London, ON}
% \begin{itemize}
% 	\item Worked in a dynamic and fast changing atmosphere, providing exceptional customer service to guests.
% 	\item Adapted to changing roles and responsibilities, accommodating the needs of the business and team members.
% 	\item Managed takeout orders and their preparation at the expo stand, ensuring timely and accurate delivery of orders to customers.
% 	\item Provided exceptional customer service through booking reservations and assisting in events booking.
% 	\item Assisted in the retail sales of beer and merchandise, ensuring a positive and informative customer experience.
% 	\item Collaborated with team members to maintain a high standard of service and a positive work environment.
% \end{itemize}
% \divider

% \cvevent{Deliveries and E-commerce Associate}{The Home Depot Canada}{March 2021 -- September 2021}{London ON}
% \begin{itemize}
% 	\item Provided exceptional customer service to customers, ensuring a positive and respectful experience.
% 	\item Managed the preparation and delivery of online orders, ensuring the accurate and timely delivery of goods.
% 	\item Assisted in the organization and maintenance of the store, ensuring a clean and organized work environment.
% 	\item Developed strong communication and teamwork skills, collaborating with team members to achieve daily goals.
% 	\item Adapted to changing roles and responsibilities, accommodating the needs of the business and team members.
% \end{itemize}

\end{document}
